\documentclass[journal, a4paper, onecolumn, draftcls]{IEEEtran} %onecolumn, draftcls
\usepackage{skieeetrans}

% TikZ libraries
\usetikzlibrary{shapes,
shapes.geometric, 
arrows.meta,
intersections, 
positioning, 
dsp, 
chains,
decorations.pathreplacing,
scopes,
fadings,
calc,
matrix,
fit,
quotes
}

\begin{document}
\title{Stable Recovery Analysis}


\maketitle

\section{Sensing Matrix}

Following \cite{mamaghanian2011compressed},
we construct a sparse binary sensing matrix $\Phi$ of size
$m \times n$.
Each column of $\Phi$ consists of exactly $d$ ones and
$m-d$ zeros, where the position of ones has been randomly
selected in each column.
Sparse binary sensing matrices can be treated as adjacency 
matrix representations of bipartite graphs.
In the equation $\by = \Phi \bx$, let $\bx$
and $\by$ represent node sets $U$ and $V$
respectively where each node in the node-set
corresponds to a component of the vector.
Consider the bipartite graph $G (\Phi) = (U, V, E)$
\footnote{$U$ and $V$ are left and right nodes of $G$
and $E$ is the set of edges between the left and right nodes.}
such that
an edge $(i, j)$ belongs to $E$ if and only if
$\Phi(j, i) = 1$. Informally, such a graph is
an expander \cite{gilbert2010sparse}
if each small subset of nodes in $U$ has many neighbors
in $V$. We refer to $U$ as the left part and $V$
as the right part of the graph $G$.
A bipartite graph is called left $d$-regular
if every node in the left part has exactly
$d$ neighbors in the right part. This corresponds to having
exactly $d$ ones in each column of $\Phi$.
A bipartite left-$d$ regular graph $G = (U, V, E)$
is called a $(k, d, \epsilon)$-expander if any
set $S \subset U$ of at most $k$ left nodes has
at least $(1-\epsilon)d|S|$ neighbors.

Sparse binary sensing matrices cannot satisfy the standard RIP
property \cite{candes2008restricted},
however, they do satisfy a generalized
RIP-p property \cite{gilbert2010sparse}.
An $m \times n$ matrix $\Phi$ is said to satisfy
RIP ($p, k, \delta$) if for any $k$-sparse vector
$\bx$, we have

\begin{equation}
\| \bx \|_p (1 - \delta) \leq \| \Phi \bx \|_p \leq \| \bx \|_p.
\end{equation}
The adjacency matrices of expander graphs have
this property. Gilbert et al. show in \cite{gilbert2010sparse}
that if $\Phi$ is the adjacency matrix of a $(k,d, \epsilon)$
expander graph $G = (U, V, E)$, then the scaled matrix
$\Phi / d$ satisfies RIP $(1,k, \delta)$ property for
$\delta = 2 \epsilon$.
They further show that for an expander matrix $\Phi$,
for any signal $\bx$, given $\by = \Phi \bx$, we
can recover $\hat{\bx}$ such that

$$
\| \bx - \hat{\bx} \|_1 \leq c(\epsilon) \| \bx - \bx_{|k} \|_1
$$
where $\bx_{|k}$ is the best $k$-term approximation of $\bx$
and $c(\epsilon)$ is a constant depending on $\epsilon$.
These theoretical results are the foundation of our encoder
design wherein a bounded quantization noise doesn't impact
the reconstruction quality. 

Mamaghanian et al. \cite{mamaghanian2011compressed}
studied the variation of reconstruction SNR with $d$ for SPGL1
algorithm \cite{van2009probing}.
They chose a value of $d=12$ below which
SPGL1 recovery suffered. Zhang et al. \cite{zhang2012compressed}
showed experimentally that the BSBL-BO algorithm can do good
recovery for much lower values of $d$.
In our experiments, we have reported results for both $d=12$
as well as $d=4$.



$$
\err_q^k(\bx) = \min_{\bx' \in \Sigma_k} \| \bx - \bx' \|_q.
$$

Goal:
$$
\| \bx - \hat{\bx} \|_p \leq c \err_q^k(\bx).
$$


$G = (U, V, E)$. $E \subset U \times V$.
$\Phi \in \RR^{m \times n}$. $|U| = n$, $|V| = m$.
$U = \{ x_1, \dots, x_n \}$.
$V = \{y_1, \dots, y_n \}$.
$(i, j) \in G$ if and only if $\Phi(i, j) = 1$.


$(k, d, \epsilon)$ expander: $S \subset U$ of at most $k$
nodes has at least $(1 - \epsilon)d |S|$ nodes. 

We need $|V| < d |U|$. Every column of $\Phi$
as at most $d$ ones. Hence, we can reach at-most
$d |U|$ nodes in $V$. If $|V| \geq d |U|$, 
then the number of neighbors of all $U$ nodes
is bounded by $d |U|$. Some nodes in $V$ may
not be reachable at all.
Assume that $|V| < d |U|$. Then the number of
neighbors is bounded by:

$$
d | S | \leq | V|  < d |U|.
$$




\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{IEEEabrv,references}

\end{document}
